[WIP] Church Bells are Not Ringing: Decrease in the Opposite-Sex and Same-Sex Couples Opting for Religous Marriage Ceremonies in England and Wales

### 2024-04-24 paper/paper.qmd
paper update

## Load packages
library(tinytex)
library(tidyverse)
library(ggplot2)
library(knitr)
library(arrow)

@@

## Data Cleaning
The data set was imported into RStudio where the open-source statistical programming language, R [@citeR], was used for cleaning and analysis.  Data was simulated with the functionalities of the `tibble` [@tibble] package. The raw data set was extracted and saved with the functionalities of the `readr` [@readr], `tidyverse` [@tidyverse], and `readxl` [@readxl] packages. Data cleaning was aided by the use of the `tidyverse` [@tidyverse], `janitor` [@janitor], `arrow` [@arrow], and `naniar` [@naniar] packages. To create tables and graphs for data visualization of the datasets, the `ggplot2` [@ggplot2] and `knitr` [@knitr] packages were used in tandem with `tinytex` [@tinytex] to create the paper format.

@@

## Opposite-Sex Civil versus Religious Ceremonies
```{r}
#| message: false
#| echo: false
#| warning: false
#| label: fig-oppositecivilvsreligious
#| fig-pos: "H"
#| fig-cap: Annual Amount of Civil (Red) and Religious (Blue) Ceremonies Between 1970 to 2020 in England and Wales for Opposite-Sex Couples
ggplot(opposite_sex, aes(x = year)) + 
  geom_line(aes(y = all_civil), color = "darkred") + 
  geom_line(aes(y = all_religious), color="steelblue")  +
  theme_minimal() +
  scale_x_continuous(breaks = seq(1970, 2020, 5)) +
  scale_y_continuous(breaks = seq(0, 300000, 20000))+
  labs(x = "Year", y = "Number of Ceremonies Conducted")
```

@@

## Same-Sex Civil versus Religious Ceremonies
```{r}
#| message: false
#| echo: false
#| warning: false
#| label: fig-samecivilvsreligious
#| fig-pos: "H"
#| fig-cap: Annual Amount of Civil (Red) and Religious (Blue) Ceremonies Between 2014 and 2020 in England and Wales for Same-Sex Couples
ggplot(same_sex, aes(x = year)) + 
  geom_line(aes(y = all_civil), color = "darkred") + 
  geom_line(aes(y = all_religious), color="steelblue")  +
  theme_minimal() +
  scale_x_continuous(breaks = seq(2014, 2020, 1)) +
  scale_y_continuous(breaks = seq(0, 8000, 500))+
  labs(x = "Year", y = "Number of Ceremonies Conducted")
```

@@

# Discussion {#sec-discussion}
## First discussion point {#sec-first-point}
## Second discussion point
## Third discussion point
## Weaknesses and Future Research {#sec-future}

>>>>

## Load packages
library(tinytex)
library(tidyverse)
library(ggplot2)
library(knitr)
library(arrow)
library(tidyr)

@@

## Data Cleaning
The data set was imported into RStudio where the open-source statistical programming language, R [@citeR], was used for cleaning and analysis.  Data was simulated with the functionalities of the `tibble` [@tibble] package. The raw data set was extracted and saved with the functionalities of the `readr` [@readr], `tidyverse` [@tidyverse], and `readxl` [@readxl] packages. Data cleaning was aided by the use of the `tidyverse` [@tidyverse], `janitor` [@janitor], `arrow` [@arrow], and `naniar` [@naniar] packages. To create tables and graphs for data visualization of the datasets, `ggplot2` [@ggplot2], `tidyr` [@tidyr], and `knitr` [@knitr] packages were used in tandem with `tinytex` [@tinytex] to create the paper format.

@@

## Opposite-Sex Civil versus Religious Ceremonies
```{r}
#| message: false
#| echo: false
#| warning: false
#| label: fig-oppositecivilvsreligious
#| fig-pos: "H"
#| fig-cap: Annual Amount of Civil (Red) and Religious (Blue) Ceremonies Between 1970 to 2020 in England and Wales for Opposite-Sex Couples

ggplot(opposite_sex, aes(x = year)) + 
  geom_line(aes(y = all_civil), color = "darkred") + 
  geom_line(aes(y = all_religious), color="steelblue")  +
  theme_minimal() +
  scale_x_continuous(breaks = seq(1970, 2020, 5)) +
  scale_y_continuous(breaks = seq(0, 300000, 20000))+
  labs(x = "Year", y = "Number of Ceremonies Conducted")
```

@@

## Same-Sex Civil versus Religious Ceremonies
```{r}
#| message: false
#| echo: false
#| warning: false
#| label: fig-samecivilvsreligious
#| fig-pos: "H"
#| fig-cap: Annual Amount of Civil (Red) and Religious (Blue) Ceremonies Between 2014 and 2020 in England and Wales for Same-Sex Couples

ggplot(same_sex, aes(x = year)) + 
  geom_line(aes(y = all_civil), color = "darkred") + 
  geom_line(aes(y = all_religious), color="steelblue")  +
  theme_minimal() +
  scale_x_continuous(breaks = seq(2014, 2020, 1)) +
  scale_y_continuous(breaks = seq(0, 8000, 500))+
  labs(x = "Year", y = "Number of Ceremonies Conducted")
```

@@

## Opposite-Sex Religious Ceremony Type
```{r}
#| message: false
#| echo: false
#| warning: false
#| label: fig-oppositereligioustype
#| fig-pos: "H"
#| fig-cap: Annual Amount of Church of England, Roman Catholic, Other Christian Denominations, and Other Relgion Ceremonies Conducted Between 1970 and 2020 in England and Wales for Opposite-Sex Couples

ggplot(opposite_sex, aes(x = year)) + 
  geom_line(aes(y = coe), color = "darkred") + 
  geom_line(aes(y = rc), color="steelblue")  +
  geom_line(aes(y = other_christian), color="darkgreen")  +
  geom_line(aes(y = other_religion), color="darkviolet")  +
  theme_minimal() +
  scale_x_continuous(breaks = seq(1970, 2020, 5)) +
  scale_y_continuous(breaks = seq(0, 175000, 15000))+
  labs(x = "Year", y = "Number of Ceremonies Conducted")
```

## Same-Sex Couple Demographics
```{r}
#| message: false
#| echo: false
#| warning: false
#| label: fig-samesexdemographics
#| fig-pos: "H"
#| fig-cap: Annual Amount of Marriage Ceremonies Conducted Between 2014 and 2020 in England and Wales for Opposite-Sex Couples by Sex

same_sex_demographics <-
  pivot_longer(same_sex, cols = c(male, female), names_to = "Sex", values_to = "Count")

ggplot(same_sex_demographics, aes(x = year, y = Count, fill = Sex)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(x = "Year",
       y = "Number of Married Couples") +
  scale_fill_manual(values = c("darkred", "steelblue"),
                    labels = c("Female", "Male")) +
  theme_minimal() +
  scale_y_continuous(breaks = seq(0, 4000, 500))
```

## Same-Sex 
# Discussion {#sec-discussion}
## First discussion point {#sec-first-point}
## Second discussion point
## Third discussion point
## Weaknesses and Future Research {#sec-future}
